---
title: "Music Insights"
author: "Kyle Kirk"
output: html_notebook
---


We need to use the tidyverse for our data and manipulation

```{r}
install.packages("tidyverse")
library("tidyverse")

survey <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/music-survey.csv")
preferences <- read_csv("https://raw.githubusercontent.com/introdsci/MusicSurvey/master/preferences-survey.csv")
```

```{r}
library("tidyverse")
library("tidyr")
library("dplyr")
library("readr")
library("stringr")
```

We're going to be renaming all the columns to a consistent format.
```{r}
colnames(survey)[colnames(survey)=="Timestamp"] <- "time_submitted"
colnames(survey)[colnames(survey)=="First, we are going to create a pseudonym for you to keep this survey anonymous (more or less). Which pseudonym generator would you prefer?"] <- "pseudonym_generator"
colnames(survey)[colnames(survey)=="What is your pseudonym?"] <- "pseudonym"
colnames(survey)[colnames(survey)=="Sex"] <- "sex"
colnames(survey)[colnames(survey)=="Major"] <- "academic_major"
colnames(survey)[colnames(survey)=="Academic Year"] <- "academic_level"
colnames(survey)[colnames(survey)=="Year you were born (YYYY)"] <- "year_born"
colnames(survey)[colnames(survey)=="Which musical instruments/talents do you play? (Select all that apply)"] <- "insturment_list"
colnames(survey)[colnames(survey)=="Artist"] <- "favorite_song_artist"
colnames(survey)[colnames(survey)=="Song"] <- "favorite_song"
colnames(survey)[colnames(survey)=="Link to song (on Youtube or Vimeo)"] <- "favorite_song_link"
```


Now we are going to create a seperate table for the Person.

```{r}

Person <- tibble(time=survey$time_submitted, pseudonym_generator=survey$pseudonym_generator, pseudonym=survey$pseudonym, sex=survey$sex, academic_major=survey$academic_major, academic_level=survey$academic_level, year_born=survey$year_born)

```

And now a tibble for Favorite Song.
```{r}

Favorite_song <- tibble(pseudonym=survey$pseudonym, song_artist=survey$favorite_song_artist, song=survey$favorite_song, link=survey$favorite_song_link)

```


Adjust the time/date using the POSIXct.
```{r}
new_person$time <- as.POSIXct(new_person$time, format = "%m/%d/%Y %H:%M")
```


You can change the levels, as well as assign them.
```{r}
levels(Person$academic_major)
```
Will print it out

This will change it so that the lower case information systems will be changed to the upper case one and replace it in the levels as well.
```{r}
levels(Person$academic_major)[levels(Person$academic_major) == "Computer information systems"] <- "Computer Information Systems"
```


We are going to take the Ratings and make a rating table that is just Pseudoynm -- artist_song -- ratings
```{r}
new_pref <- preferences %>% gather(song_name, rating, 3:45)
```